\section{Where did you go on vacations as a child?}
Regarding taking a vacation when I was a child you have to understand that on a farm it was difficult to take time away from the care of the animals.
Cows needed to be milked and fed morning and evening.
Chickens needed to be fed and the eggs gathered morning and evening.
There was a rhythm to life on the farm that did not leave time for taking vacations.
There were two times that I remember my parents leaving the farm for a day or two.
My older siblings must have been old enough to do the chores with the help of a hired man.
We traveled in a station wagon and even without the requirement of seat belts there was only so much room for children to sit.

My memories are that the youngest five children traveled with Pop and Mom to northern Pennsylvania.
We stopped at Eagles Mere.
While my memory is of a lake where we had a picnic, my research today tells me it is a small historic town that time has forgotten.
We spent the night with Marvin and Dorothy Groff.
Marvin was Pop's cousin and they had moved to the northern part of the state to help start a church.
The main impression that has stayed with me from that trip was the adventure of seeing new places and meeting new people.

The second trip that I remember took us south to the mountains of Virginia to visit John and Anna Miller who were also working at beginning a new church.
This family had children that matched the ages of at least a portion of our family.
They had a David, Daniel, Rhoda and Martha who was my age.
Again I remember that we slept at their house and an impression that has stayed with me is the darker shadiness of where they lived in the mountains.
The shaded valley in the mountains stood in sharp contrast to the sunlit farm where I lived.

Later my parents took the three youngest, Rachel, Joe, and Esther with them on a long trip out to the west coast of the USA and back.
They stopped to visit Mom's brother, Marvin and his wife, Maryann and three children in Phoenix, AZ.
There was only room for three in the car so I stayed home with the rest of my siblings, spending some of that time with my Uncle Wilmer and Aunt Corina.

\textbf{From Tim} - Its very interesting how the practicalities of travel created sub-groupings in the family on these vacations.
It also makes sense that they could afford to travel more later in your life as a family.

I also love the impression of the shadiness of the Virginia valley in contrast to where you lived.

It's interesting that two of the three vacations were to church planters.
Was this because missionary work was the main thing in that period that led people to leave the Lancaster area while still connected to the church?

\textbf{From Mom} - Missionary work was certainly something that took people away from Lancaster County.
My parents were strong supporters of mission work.
