
Tell me about a song that brings back an interesting memory from your youth
There are two songs from my elementary school days that come to mind, My Grandfather's Clock and Old Black Joe. The first was a song that pointed to the mortality of us all. Johnny Cash sang this song.
My grandfather's clock
My grandfather's clock was too large for the shelf
So it stood ninety years on the floor
It was taller by half than the old man himself
Though it weighed not a pennyweight more
It was bought on the morn of the day that he was born
And was always his treasure and pride
But it stopped, short never to go again
When the old man died
Ninety years without slumbering
His life seconds numbering
It stopped, short never to go again
When the old man died
My grandfather said that of those he could hire
Not a servant so faithful he found
For it wasted no time and had but one desire
At the close of each week to be wound
And it kept in its place, not a frown upon its face
And its hands never hung by its side
But it stopped short, never to go again
When the old man died
It rang and alarmed in the dead of the night
An alarm that for years had been dumb
And we knew that his spirit was pluming for flight
That his hour for departure had come
Still the clock kept the time with a soft and muffled chime
As we silently stood by his side
But it stopped short, never to go again
When the old man died
Ninety years without slumbering
His life seconds numbering
It stopped short, never to go again
When the old man died
Songwriters: Erich Doll / Henry Clay Work
The second is a Stephen Foster song that reminded me of the hard lives of the negro slaves.
1. Gone are the days when my heart was young and gay, Gone are my friends from the cotton fields away, Gone from the earth to a better land I know, I hear their gentle voices calling "Old Black Joe" . 
Chorus I'm coming, I'm coming, for my head is bending low: I hear their gentle voices calling, "Old Black Joe". 
2. Why do I weep when my heart should feel no pain Why do I sigh that my friends come not again, Grieving for forms now departed long ago. I hear their gentle voices calling "Old Black Joe". Chorus 
3. Where are the hearts once so happy and so free? The children so dear that I held upon my knee, Gone to the shore where my soul has longed to go. I hear their gentle voices calling "Old Black Joe" . Chorus
The third is a song that should I hear it or sing it would remind me of the day that I left home for three years in Honduras. My family gathered for a time of farewell and my mother asked people to offer songs for us to sing. My brother Dave with whom I had some issues suggested Under His Wings. I was surprised and realized that perhaps he did care about me and what was happening in my life. 
Under His Wings
1.Under His wings I am safely abiding;
    Though the night deepens and tempests are wild,
Still I can trust Him, I know He will keep me;
    He has redeemed me, and I am His child. 
Chorus: Under His wings, under His wings,
    Who from His love can sever?
Under His wings my soul shall abide,
    Safely abide forever. 
2. Under His wings--what a refuge in sorrow!
    How the heart yearningly turns to His rest!
Often when earth has no balm for my healing,
    There I find comfort, and there I am blest. 
3. Under His wings--oh, what precious enjoyment!
    There will I hide till life's trials are o'er;
Sheltered, protected, no evil can harm me;
    Resting in Jesus I'm safe evermore.





