\section{Are you still friends with any of your friends from high school? How have they changed since then?}
Sorry to say I am not in contact with friends from high school.
However I do keep in contact with two women with whom I shared an apartment as a young adult.
Sandi Bontrager Harnish and Rose Brubaker Kennel.
We shared an apartment from fall of 1977 to summer of 1979.

Sandi grew up in northern Indiana and married a Lancaster County farmer, Martin Harnish.
She lives a few miles from the farm where I grew up.
You might say that we switched places since I now live in northern Indiana some miles from where she grew up.

Sandi and Martin have two children.
The oldest, Amanda is a few weeks older than Tim.
Sandi and I traded baby due dates and Amanda was born mid-April while Tim waited until early May to be born.
While we went through the pregnancy at the same time I expected to have my baby first but the babies did not agree and made the trade.

Daniel, their second child was born the same year as Abby.
So while our children were small Sandi and I saw each other at mother's groups.

Rose married John's friend, Chris Kennel.
She taught school for many years and then pre-school.
Rose and Chris have two children, Eric and Carmen.
Eric and Tim are the same age and Carmen was between Abby and Jonathan.
We have memories of a weekend spent with them at their cabin in the Pennsylvania Mountains.

We enjoy connecting with these couples when we spend time in Lancaster County and time permits.
They have both hosted us as well.

Lois, Rose, and Sandi

Amanda and Tim

Eric and Tim





