\section{What's the first major news story you can remember living through as a child?}
It is hard to remember what the first major news story that impressed itself on my mind was.
I used a timeline of news during the decade of the 50s to jog my memory.

I do remember that Eisenhower was president of the United States when I was born and was re-elected when I was 4 years old.
Having a military general for a president was normalized for me because that is how it was when I first learned about government.

I learned about Rosa Parks but I do not remember hearing much conversation about civil rights and the demonstrations that were impacting our country.

Ray Kroc opened the first MacDonald's restaurant when I was 3 years old and I was likely close to 10 years old when I made my first visit to the first MacDonald's restaurant in Lancaster city.
Our hired man took us.
My parents were traveling so he filled his car with those of us who fit and we went to the restaurant on Columbia Avenue.
I think that I had a hamburger and milk shake.

I do have memories of the presidential election of 1960.
I was likely in 4th grade.
One of the controversies of the situation was the question - what changes would a Catholic president make in our world.
I was impressed by the young couple that moved into the White House.

I knew about the race to space and learned more about it by paging through the Life magazines at my Aunties house.

I have hardly any memories and little awareness of the Cuban crisis or the beginnings of the Vietnam War.

It was probably the assassination of President Kennedy in Dallas, Texas November 22, 1963 that I remember living through as a child.
I was eleven years old.
The fact that the assassination marks the first 24-hour coverage of a major news event by the major networks made it hard to not hear about and feel the impact of these events.
Recently I heard someone describe how she was watching live TV when Jack Ruby shot and killed Lee Harvey Oswald.
I did not have that experience but I do remember staring at the photo of that event in the pages of Life Magazine.
I believe that our family had a radio by that time.

In 1964 again thanks to the Life magazine I knew that the Beatles arrived in the USA for a visit.
I thought they looked strange and their music was not at all what I was used to hearing.






