\section{How did you get your first job?}
I got my first job by following my older brothers and sisters to a neighboring farm to pick strawberries.
I'm not sure how old I was but I do remember that the strawberry rows seems awfully long.
We were paid per quart box picked and I think that I was paid with change.
We walked from home to the strawberry patch and back again.
I probably slept well after a day of picking.
That was child labor but that was also life on a farm.

My second job was likely the one I had cleaning for a lady who lived nearby.
I was following in the footsteps of older sisters who worked this job before me.
This family was part of the Shenk's Cup Cheese family business.
The founder had two sons and a daughter who worked with him.
In the house that I cleaned there were two boys, but they were not expected to clean the house.
Elise was the woman's name and she had clear expectations for what and how a house should be cleaned.
I learned how to clean in a systematic way that benefited me for a life of cleaning.
Sorry if I did not pass that skill on to my children.

From Tim - Hah! I love the last sentence there.
I promise that it was not for lack of trying on your part.
I was reminded yesterday that I did learn to fold sheets when doing laundry.
This summer instead of using the dryer we've been hanging our laundry out on the line in the hot sun to save a little electricity.
So small steps in domesticity.

Also, in my involvement in the campaign around the farmworker's bill of rights, I hadn't made the connection that you grew up doing this work as well.
It's a different context, but similar in some way.
I guess my first job was detassling corn.
It's funny that I have so minimal memories of that.






