9 Did you get along with your siblings as a child?
As a young adult I remember my mother telling me that I was an "easy" child.
I suppose she meant that I did not take up much of her time.
Given all that a mother of eleven children had to do, one can see why she used the word easy to describe a child with a quiet reserved personality.
I think that I got along well with my siblings.

My oldest brother is ten years older than me and so I do not remember spending much time playing or interacting with the older half of my family.
There was always work to be done on the farm.
During harvesting time we might spend several afternoons a week helping to preserve fruit or vegetables.
We each had our daily chores to do.
I did not like that an older brother hit me with a rubber hose in a work situation.
That did not help create a positive open attitude toward my older siblings.

However, the younger of us children were four girls and one boy.
We played together setting up house with our dolls on the four porches of the farm house.
We washed and hung up our dolly clothes.
There was a small shed used for rabbit hutches.
When it was empty we turned it into a "playhouse".
This is where we set up our school.
I remember that I found it more fun to set up the school that it was to actually play school.
Older siblings created tunnels through the haymow.
It was a somewhat scary adventure to play tag inside the tunnel.
Summer evenings we often played a game of beacon.
Winter evenings and Sunday afternoons were times when our mother read aloud to us.

So I spent a lot of time with siblings.
When there were disagreements, and there were, slapping was often the signal that someone was upset at another.
That was not acceptable behavior and could result in a parental reprimand to the offending party/ies.
I think that I cried easily and may have used that to indicate my unhappiness and scare off someone who was upset at me.





